Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-16 paper.tex
intro and method

Fuel cycle simulations, as any simulation process, do not produce results
without errors.  Those errors have different sources: data uncertainties (when
the simulation relies on previously estimated/measured metrics), modeling
uncertainties (produced by the simplification made by the simulator) and the
``operational`` uncertainty (uncertainty on the operation parameters of the
different facilities).

Some treaty verification scenarios require estimating historical fissile
material production based on records of facility operation and material
transfer.  If the measurements of facility operation and material transfer are
subject to uncertainty, the total production quantities will then also be
uncertain, creating an opportunity for undetected diversion.  This study seeks
to understand which measures of facility operation have the most impact on the
uncertainty of fissile material production across a complete fuel cycle.  An
approaching using Total Monte Carlo methodology will be applied to the Cyclus
fuel cycle simulator \cite{cyclus} to estimate output metrics uncertainty caused
by individual facility uncertainties.

@@

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations.  For each deployed facilities, the uncertainty associated
parameters have been a normally distributed with an artificially large standard
deviation of $10\%$.

To pursuit this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the
CyCLASS\footnote{Reactor and Fuel fabrication facility based on
    CLASS\cite{CLASS}  models} have been
updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
operational parameters of their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all modification implemented in the
range of facilities present in Cycamore and CyCLASS.

\begin{table}[htb]
\centering
  \caption{Summary of facility modification per source package.}
\begin{tabular}{cll}
\toprule

@@

The uncertainty on the different parameters have been considered for this study
as systematic for each new deployed facilities: each time a new facility is
deployed (such as a reactor or a fuel fabrication facility) a new set a
parameter is computed.

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation.  In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to a fuel enrichment uncertainty close to
$10\%$.

>>>>

Fuel cycle simulations, as with any simulation process, do not produce results
without errors.  Those errors have different sources: data uncertainties (from
the simulator's reliance on previously estimated/measured metrics), modeling
uncertainties (from simplifications made by the simulator) and the
``operational`` uncertainty (from the operation parameter uncertainties of
different facilities).

Simulation errors are important in the context of treaty verification. 
Some scenarios require estimating historical fissile
material production based on records of facility operation and material
transfer.  If the measurements of facility operation and material transfer are
subject to uncertainty, the total production quantities will then also be
uncertain, creating an opportunity for undetected diversion.  This study seeks
to understand which measures of facility operation have the most impact on the
uncertainty of fissile material production across a complete fuel cycle.
To accomplish this, a Total Monte Carlo methodology will be applied to the Cyclus
fuel cycle simulator \cite{cyclus} to estimate the effect of individual facility uncertainties on the output metrics.

@@

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the standard deviation of the output metrics over about 200
different simulations.  For each deployed facility, the
parameters are normally distributed with an artificially large standard
deviation of $10\%$.

To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the
CyCLASS\footnote{Reactor and fuel fabrication facility based on
    CLASS\cite{CLASS}  models} were
updated\cite{mouginot_2018, cyclass} to evaluate uncertainty of several
operational parameters in their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
facilities of Cycamore and CyCLASS.

\begin{table}[htb]
\centering
  \caption{Summary of facility modifications according to their source package.}
\begin{tabular}{cll}
\toprule

@@

The uncertainty of the different parameters in this study
are systematic for each new deployed facility: each time a new facility is
deployed (such as a reactor or a fuel fabrication facility) a new set of
parameters are computed.

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
enrichment is not applied directly to the effective enrichment. It is instead applied to the
burnup, which leads to a fuel enrichment uncertainty close to
$10\%$.
